### 2013-12-18 manuscripts/dpp-msbayes/dpp-msbayes-main.tex
Updating dpp manuscript.
Correcting posterior distribution equations. Making the marginal
likelihood (denominator) of Bayes rule conditional on the parameters
that are fixed by the user.
Updating DPP manuscript.
Adding subsection placeholders for empirical analyses of the Philippines
data in both Methods and Results.
Working on dpp ms.
In the process of integrating new figures into the text, and removing
old figures... A ways to go yet.

\begin{linenomath}
With \alignmentVector, \hkyModelVector, \ploidyScalarVector, and
\mutationRateScalarConstantVector in hand, the joint posterior distribution
of our model is given by
\begin{equation}
    p(\geneTreeVector, \divTimeMapVector, \demographicParamVector, 
    \locusMutationRateScalarVector, \locusRateHetShapeParameter \given
    \alignmentVector, \hkyModelVector, \ploidyScalarVector,
    \mutationRateScalarConstantVector) =
    \frac{p(\alignmentVector \given \geneTreeVector, \divTimeMapVector,
        \demographicParamVector, \locusMutationRateScalarVector,
        \locusRateHetShapeParameter, \hkyModelVector, \ploidyScalarVector,
        \mutationRateScalarConstantVector)
        p(\geneTreeVector, \divTimeMapVector, \demographicParamVector,
        \locusMutationRateScalarVector, \locusRateHetShapeParameter \given
        \hkyModelVector, \ploidyScalarVector,
        \mutationRateScalarConstantVector)}{
        p(\alignmentVector)},
    \label{eq:fullModelCompactJoint}
\end{equation}
which can be expanded out into components that are assumed to be independent
to get
\begin{equation}
    p(\geneTreeVector, \divTimeMapVector, \demographicParamVector, 
    \locusMutationRateScalarVector, \locusRateHetShapeParameter \given
    \alignmentVector, \hkyModelVector, \ploidyScalarVector,
    \mutationRateScalarConstantVector) =
    \frac{p(\alignmentVector \given \geneTreeVector, \hkyModelVector)
        p(\geneTreeVector \given \divTimeMapVector, \demographicParamVector,
        \locusMutationRateScalarVector, \ploidyScalarVector,
        \mutationRateScalarConstantVector)
        p(\locusMutationRateScalarVector \given \locusRateHetShapeParameter)
        p(\locusRateHetShapeParameter)
        p(\divTimeMapVector)
        p(\demographicParamVector)}{
        p(\alignmentVector)},
    \label{eq:fullModelCompact}
\end{equation}
where
$\divTimeMapVector = (\divTimeMap{1}, \ldots, \divTimeMap{\npairs{}})$
is a vector of population divergence times for each of the \npairs{} pairs of
populations,
$\demographicParamVector = (\demographicParams{1}, \ldots,
\demographicParams{\npairs{}})$
is a vector of the demographic parameters for each of the \npairs{} population
pairs,
$\locusMutationRateScalarVector = (\locusMutationRateScalar{1}, \ldots
\locusMutationRateScalar{\nlociTotal})$
is a vector of locus-specific mutation-rate scaling parameters for each of the
\nlociTotal loci,
\locusRateHetShapeParameter is the shape parameter of a gamma-distributed
prior on \locusMutationRateScalar{}, and
$p(\alignmentVector)$ is the probability of the data (or the marginal
likelihood of the model).
\end{linenomath}

\begin{linenomath}
To avoid calculating the likelihood terms of Equation \ref{eq:fullModelCompact},
we distill each sequence alignment \alignment{}{} into a vector of insufficient
summary statistics \alignmentSS{}{}, thus replacing the full dataset
$\alignmentVector = (\alignment{1}{1}, \ldots,
    \alignment{\npairs{}}{\nloci{\npairs{}}})$
with vectors of summary statistics for each alignment
$\ssVectorObs = (\alignmentSSObs{1}{1}, \ldots,
    \alignmentSSObs{\npairs{}}{\nloci{\npairs{}}})$.
For each population pair, the means of the summary statistics are calculated
across the \nloci{} loci, reducing the vector to
$\ssVectorObs = (\alignmentSSObs{1}{}, \ldots,
    \alignmentSSObs{\npairs{}}{})$.
This allows us to estimate the approximate joint posterior distribution
{\small
\begin{equation}
    p(\geneTreeVector, \divTimeMapVector, \demographicParamVector, 
    \locusMutationRateScalarVector, \locusRateHetShapeParameter \given
    \ssSpace, \hkyModelVector, \ploidyScalarVector,
    \mutationRateScalarConstantVector) =
    \frac{p(\ssSpace \given \geneTreeVector, \hkyModelVector)
        p(\geneTreeVector \given \divTimeMapVector, \demographicParamVector,
        \locusMutationRateScalarVector, \ploidyScalarVector,
        \mutationRateScalarConstantVector)
        p(\locusMutationRateScalarVector \given \locusRateHetShapeParameter)
        p(\locusRateHetShapeParameter)
        p(\divTimeMapVector)
        p(\demographicParamVector)}{
        p(\ssSpace)},
    \label{eq:approxModelCompact}
\end{equation}
}
where \ssSpace is the multidimensional Euclidean space around the vector of
summary statistics, the radius of which is the tolerance \tol.
The sources of approximation are the insufficiency of the statistics and the
\tol being greater than zero.
We describe the full model in detail before delving into the numerical
method of estimating the approximate model.
\end{linenomath}

@@

\section*{Results}
\subsection*{Validation analyses: Estimation accuracy}
In terms of estimating summary statistics of model parameters (\divTimeNum,
\divTimeDispersion, and \divTimeMean), the \modelDPP performs similarly when
applied to datasets generated under all four models of Table \ref{tabPriors}
(Figs.\
\labelcref{figValidationAccuracyDPPDPP,figValidationAccuracyUniformDPP,figValidationAccuracyOldDPP,figValidationAccuracyUshapedDPP}).
The same is true for models \modelUniform (Figs.\
\labelcref{figValidationAccuracyDPPUniform,figValidationAccuracyUniformUniform,figValidationAccuracyOldUniform,figValidationAccuracyUshapedUniform})
and \modelUshaped (Figs.\
\labelcref{figValidationAccuracyDPPUshaped,figValidationAccuracyUniformUshaped,figValidationAccuracyOldUshaped,figValidationAccuracyUshapedUshaped}).
All three of the models with exponential priors on nuisance parameters
(\modelDPP, \modelUniform, and \modelUshaped) perform well when applied
to the data generated under the original \msb model, \modelOld (Figs.\
\labelcref{figValidationAccuracyOldDPP,figValidationAccuracyOldUniform,figValidationAccuracyOldUshaped}).
The \modelOld model also performed well on its own datasets (Figure
\ref{figValidationAccuracyOldOld}), but performed poorly when applied to the
data generated under the other three models (Figs.\
\labelcref{figValidationAccuracyDPPOld,figValidationAccuracyUniformOld,figValidationAccuracyUshapedOld}).
Thus, the newly implemented models display greater robustness than
the original model.

Posterior adjustment with GLM regression does improve the estimation
accuracy for the continuous variables \divTimeDispersion and \divTimeMean,
however, this is not always true for estimating the discrete variable
\divTimeNum (Figs.\
\labelcref{figValidationAccuracyDPPDPP,figValidationAccuracyUniformDPP,figValidationAccuracyOldDPP,figValidationAccuracyUshapedDPP,figValidationAccuracyDPPUniform,figValidationAccuracyUniformUniform,figValidationAccuracyOldUniform,figValidationAccuracyUshapedUniform,figValidationAccuracyDPPUshaped,figValidationAccuracyUniformUshaped,figValidationAccuracyOldUshaped,figValidationAccuracyUshapedUshaped,figValidationAccuracyDPPOld,figValidationAccuracyUniformOld,figValidationAccuracyUshapedOld,figValidationAccuracyOldOld}).

\subsection*{Validation analyses: Model-choice accuracy}
The \msb model, and our modification of it, is a model-choice method
with the primary purpose of estimating the probabilities of models
of divergence across taxa.
Thus, it is critical to assess the method's ability to accurately
estimate the posterior probabilities of divergence models.
Our results demonstrate that the unadjusted estimates of divergence models are
generally more accurate than the regression-adjusted estimates, especially when
using $\divTimeDispersion < 0.01$ to assess the probability of the one
divergence model (Figs.\
\labelcref{figValidationModelChoiceDPPDPP,figValidationModelChoiceUniformDPP,figValidationModelChoiceOldDPP,figValidationModelChoiceUshapedDPP,figValidationModelChoiceDPPUniform,figValidationModelChoiceUniformUniform,figValidationModelChoiceOldUniform,figValidationModelChoiceUshapedUniform,figValidationModelChoiceDPPUshaped,figValidationModelChoiceUniformUshaped,figValidationModelChoiceOldUshaped,figValidationModelChoiceUshapedUshaped,figValidationModelChoiceDPPOld,figValidationModelChoiceUniformOld,figValidationModelChoiceUshapedOld,figValidationModelChoiceOldOld}).
Thus, we will focus our discussion of the results on the unadjusted estimates.

The model-choice behavior of the \modelDPP is relatively accurate when applied
to datasets generated under models \modelDPP, \modelUniform, and \modelOld
(Figs.\
\labelcref{figValidationModelChoiceDPPDPP,figValidationModelChoiceUniformDPP,figValidationModelChoiceOldDPP}).
It is less accurate and tends to underestimate the probability of the
one-divergence model when applied to the data generated under \modelUshaped
(Figure \ref{figValidationModelChoiceUshapedDPP}).
The \modelUniform model performs almost identically as \modelDPP in
terms of model-choice accuracy (Figs.\
\labelcref{figValidationModelChoiceDPPUniform,figValidationModelChoiceUniformUniform,figValidationModelChoiceOldUniform,figValidationModelChoiceUshapedUniform}).

@@

>>>>

\begin{linenomath}
With \alignmentVector, \hkyModelVector, \ploidyScalarVector, and
\mutationRateScalarConstantVector in hand, the joint posterior distribution
of our model is given by
\begin{equation}
    p(\geneTreeVector, \divTimeMapVector, \demographicParamVector, 
    \locusMutationRateScalarVector, \locusRateHetShapeParameter \given
    \alignmentVector, \hkyModelVector, \ploidyScalarVector,
    \mutationRateScalarConstantVector) =
    \frac{p(\alignmentVector \given \geneTreeVector, \divTimeMapVector,
        \demographicParamVector, \locusMutationRateScalarVector,
        \locusRateHetShapeParameter, \hkyModelVector, \ploidyScalarVector,
        \mutationRateScalarConstantVector)
        p(\geneTreeVector, \divTimeMapVector, \demographicParamVector,
        \locusMutationRateScalarVector, \locusRateHetShapeParameter \given
        \hkyModelVector, \ploidyScalarVector,
        \mutationRateScalarConstantVector)}{
        p(\alignmentVector \given \hkyModelVector, \ploidyScalarVector,
        \mutationRateScalarConstantVector)},
    \label{eq:fullModelCompactJoint}
\end{equation}
which can be expanded out into components that are assumed to be independent
to get
\begin{equation}
    p(\geneTreeVector, \divTimeMapVector, \demographicParamVector, 
    \locusMutationRateScalarVector, \locusRateHetShapeParameter \given
    \alignmentVector, \hkyModelVector, \ploidyScalarVector,
    \mutationRateScalarConstantVector) =
    \frac{p(\alignmentVector \given \geneTreeVector, \hkyModelVector)
        p(\geneTreeVector \given \divTimeMapVector, \demographicParamVector,
        \locusMutationRateScalarVector, \ploidyScalarVector,
        \mutationRateScalarConstantVector)
        p(\locusMutationRateScalarVector \given \locusRateHetShapeParameter)
        p(\locusRateHetShapeParameter)
        p(\divTimeMapVector)
        p(\demographicParamVector)}{
        p(\alignmentVector \given \hkyModelVector, \ploidyScalarVector,
        \mutationRateScalarConstantVector)},
    \label{eq:fullModelCompact}
\end{equation}
where
$\divTimeMapVector = (\divTimeMap{1}, \ldots, \divTimeMap{\npairs{}})$
is a vector of population divergence times for each of the \npairs{} pairs of
populations,
$\demographicParamVector = (\demographicParams{1}, \ldots,
\demographicParams{\npairs{}})$
is a vector of the demographic parameters for each of the \npairs{} population
pairs,
$\locusMutationRateScalarVector = (\locusMutationRateScalar{1}, \ldots
\locusMutationRateScalar{\nlociTotal})$
is a vector of locus-specific mutation-rate scaling parameters for each of the
\nlociTotal loci,
\locusRateHetShapeParameter is the shape parameter of a gamma-distributed
prior on \locusMutationRateScalar{}, and
$p(\alignmentVector)$ is the probability of the data (or the marginal
likelihood of the model).
\end{linenomath}

\begin{linenomath}
To avoid calculating the likelihood terms of Equation \ref{eq:fullModelCompact},
we distill each sequence alignment \alignment{}{} into a vector of insufficient
summary statistics \alignmentSS{}{}, thus replacing the full dataset
$\alignmentVector = (\alignment{1}{1}, \ldots,
    \alignment{\npairs{}}{\nloci{\npairs{}}})$
with vectors of summary statistics for each alignment
$\ssVectorObs = (\alignmentSSObs{1}{1}, \ldots,
    \alignmentSSObs{\npairs{}}{\nloci{\npairs{}}})$.
For each population pair, the means of the summary statistics are calculated
across the \nloci{} loci, reducing the vector to
$\ssVectorObs = (\alignmentSSObs{1}{}, \ldots,
    \alignmentSSObs{\npairs{}}{})$.
This allows us to estimate the approximate joint posterior distribution
{\small
\begin{equation}
    p(\geneTreeVector, \divTimeMapVector, \demographicParamVector, 
    \locusMutationRateScalarVector, \locusRateHetShapeParameter \given
    \ssSpace, \hkyModelVector, \ploidyScalarVector,
    \mutationRateScalarConstantVector) =
    \frac{p(\ssSpace \given \geneTreeVector, \hkyModelVector)
        p(\geneTreeVector \given \divTimeMapVector, \demographicParamVector,
        \locusMutationRateScalarVector, \ploidyScalarVector,
        \mutationRateScalarConstantVector)
        p(\locusMutationRateScalarVector \given \locusRateHetShapeParameter)
        p(\locusRateHetShapeParameter)
        p(\divTimeMapVector)
        p(\demographicParamVector)}{
        p(\ssSpace \given \hkyModelVector, \ploidyScalarVector,
        \mutationRateScalarConstantVector)},
    \label{eq:approxModelCompact}
\end{equation}
}
where \ssSpace is the multidimensional Euclidean space around the vector of
summary statistics, the radius of which is the tolerance \tol.
The sources of approximation are the insufficiency of the statistics and the
\tol being greater than zero.
We describe the full model in detail before delving into the numerical
method of estimating the approximate model.
\end{linenomath}

@@

\subsection*{An empirical application}
\ldots

\section*{Results}
\subsection*{Validation analyses: Estimation accuracy}
In terms of estimating the variance of divergence times (\divTimeDispersion),
the models with exponentially distributed priors (\modelUshaped, \modelUniform,
and \modelDPP) perform similarly when applied to datasets generated under all
four of the models of Table \ref{tabPriors}
(Figure~S\ref{figValidationAccuracyOmega}).
The \modelOld model performs similarly to these models when applied to its
own datasets, but is sensitive to model violations and is more biased when
applied to data generated under the other three models
(Figure~S\ref{figValidationAccuracyOmega}).
This results are similar for the GLM-adjusted estimates of \divTimeDispersion,
albeit the regression adjustment tends to improve estimates of this continuous
statistic for all the models
(Figure~S\ref{figValidationAccuracyPsiGlm}).

The same general pattern is seen for estimates of \divTimeMean, with
the all four models performing similarly when applied to the data generated
under \modelOld, the models with exponentially distributed priors performing
similarly when applied to data generated under other models, and the
\modelOld is more biased when applied to data generated under other models
(Figure~S\ref{figValidationAccuracyTime}).
Also, the regression adjustment tends to slightly improve estimates of
this continuous statistic for all of the models
(Figure~S\ref{figValidationAccuracyTimeGlm}).

In terms of estimating the number of divergence events (\divTimeNum), the
\modelDPP model has the lowest root mean square error (RMSE) when applied
to data generated under most of the models of Table \ref{tabPriors}
(Figure~S\ref{figValidationAccuracyPsi}).
The \modelOld model performs slightly better when applied to its own data,
but is the worst performer when applied to data generated under other models
(Figure~S\ref{figValidationAccuracyPsi}).
There is a trend of $\modelDPP > \modelUniform > \modelUshaped > \modelOld$
in terms of estimation accuracy as measured by RMSE when the models are applied
to data generated under most of the models
(Figure~S\ref{figValidationAccuracyPsi}).
Unlike for the continuous statistics, regression adjustment of this discrete
statistic tends to increase estimation bias; all of the models tend to
underestimate \divTimeDispersion after the GLM-adjustment
(Figure~S\ref{figValidationAccuracyPsiGlm}).

\subsection*{Validation analyses: Model-choice accuracy}
The \msb model, and our modification of it, is a model-choice method
with the primary purpose of estimating the probabilities of models
of divergence across taxa.
Thus, it is critical to assess the method's ability to accurately
estimate the posterior probabilities of divergence models.
Consistent with the findings of \citet{Oaks2012}, our results demonstrate that
the unadjusted estimates of divergence-model posterior probabilities are
generally more accurate than regression-adjusted estimates
(Figure~\ref{figValidationModelChoicePsi} versus
S\ref{figValidationModelChoicePsiGlm} and
Figure~\ref{figValidationModelChoiceOmega} versus
S\ref{figValidationModelChoiceOmegaGlm}).
Regression adjustment results in biased estimates of the posterior probability
of the one-divergence model when all model assumptions are satisfied, which is
well illustrated in Figure S\ref{figValidationModelChoiceOmegaGlm}.
As a result, we will focus our discussion of the results on the unadjusted
estimates.

We find that all four models accurately estimate the posterior probability of
the one-divergence model when applied to their own datasets (i.e., when the
prior is correct; see diagonal of Figures~\ref{figValidationModelChoicePsi} \&
\ref{figValidationModelChoiceOmega}).
The \modelUniform and \modelDPP show robustness to prior violations and
perform well when applied to data generated under other models
(Figures~\ref{figValidationModelChoicePsi} \&
\ref{figValidationModelChoiceOmega}).
However, both are less accurate and tends to underestimate the probability of the
one-divergence model when applied to the data generated under \modelUshaped
(Figures~\ref{figValidationModelChoicePsi} \&
\ref{figValidationModelChoiceOmega}).
The model-choice behavior of the \modelDPP is relatively accurate when applied
to datasets generated under models \modelDPP, \modelUniform, and \modelOld
(Figs.\
\labelcref{figValidationModelChoiceDPPDPP,figValidationModelChoiceUniformDPP,figValidationModelChoiceOldDPP}).
It is less accurate and tends to underestimate the probability of the
one-divergence model when applied to the data generated under \modelUshaped
(Figure \ref{figValidationModelChoiceUshapedDPP}).
The \modelUniform model performs almost identically as \modelDPP in
terms of model-choice accuracy (Figs.\
\labelcref{figValidationModelChoiceDPPUniform,figValidationModelChoiceUniformUniform,figValidationModelChoiceOldUniform,figValidationModelChoiceUshapedUniform}).

@@

\subsection*{Empirical results}
\ldots

### 2013-12-18 manuscripts/dpp-msbayes/dpp-msbayes-si-figures.tex
Working on dpp ms.
In the process of integrating new figures into the text, and removing
old figures... A ways to go yet.

%% Validation accuracy
\siFigure{../../validation/images/validation-accuracy-psi.pdf}{
    \validationAccuracyComparisonCaption{unadjusted}{\divTimeNum}
    \jitterComment
}{figValidationAccuracyPsi}

\siFigure{../../validation/images/validation-accuracy-omega.pdf}{
    \validationAccuracyComparisonCaption{unadjusted}{\divTimeDispersion}
}{figValidationAccuracyOmega}

@@

%% Validation model choice
\siFigure{../../validation/images/validation-model-choice-psi.pdf}{
    \validationModelChoiceComparisonCaption{unadjusted}{$\divTimeNum = 1$}
}{figValidationModelChoicePsi}

\siFigure{../../validation/images/validation-model-choice-psi-glm.pdf}{
    \validationModelChoiceComparisonCaption{GLM-adjusted}{$\divTimeNum = 1$}
}{figValidationModelChoicePsiGlm}

\siFigure{../../validation/images/validation-model-choice-omega.pdf}{
    \validationModelChoiceComparisonCaption{unadjusted}{$\divTimeDispersion < 0.01$}
}{figValidationModelChoiceOmega}

@@

%% Power accuracy results
\siFigure{../../power-comparison/images/old-power-omega-accuracy-6.pdf}{
    \powerAccuracyComparisonCaption{\powerSeriesOld}
}{figPowerAccuracyOld}

\siFigure{../../power-comparison/images/uniform-power-omega-accuracy-6.pdf}{
    \powerAccuracyComparisonCaption{\powerSeriesUniform}
}{figPowerAccuracyUniform}

\siFigure{../../power-comparison/images/exp-power-omega-accuracy-6.pdf}{
    \powerAccuracyComparisonCaption{\powerSeriesExp}
}{figPowerAccuracyExp}

%% Power psi results
\siFigure{../../power-comparison/images/old-power-psi-6.pdf}{
    \powerComment{\powerSeriesOld}
    \powerPsiComment{\powerSeriesOld}
    \timeConversionComment
}{figPowerPsiOld}

\siFigure{../../power-comparison/images/uniform-power-psi-6.pdf}{
    \powerComment{\powerSeriesUniform}
    \powerPsiComment{\powerSeriesUniform}
    \timeConversionComment
}{figPowerPsiUniform}

\siFigure{../../power-comparison/images/exp-power-psi-6.pdf}{
    \powerComment{\powerSeriesExp}
    \powerPsiComment{\powerSeriesExp}
    \timeConversionComment
}{figPowerPsiExp}

%% Power dispersion results
\siFigure{../../power-comparison/images/old-power-omega-6.pdf}{
    \powerComment{\powerSeriesOld}
    \powerDispersionComment{\powerSeriesOld}
    \timeConversionComment
}{figPowerPsiOld}

\siFigure{../../power-comparison/images/uniform-power-omega-6.pdf}{
    \powerComment{\powerSeriesUniform}
    \powerDispersionComment{\powerSeriesUniform}
    \timeConversionComment
}{figPowerPsiUniform}

\siFigure{../../power-comparison/images/exp-power-omega-6.pdf}{
    \powerComment{\powerSeriesExp}
    \powerDispersionComment{\powerSeriesExp}
    \timeConversionComment
}{figPowerPsiExp}

%% Power psi probability results
\siFigure{../../power-comparison/images/old-power-psi-prob-6.pdf}{
    \powerSupportComment{\powerSeriesOld}
    \powerProbComment{$p(\divTimeNum = 1 | \ssSpace)$}{\powerSeriesOld}
    \timeConversionComment
}{figPowerPsiOld}

\siFigure{../../power-comparison/images/uniform-power-psi-prob-6.pdf}{
    \powerSupportComment{\powerSeriesUniform}
    \powerProbComment{$p(\divTimeNum = 1 | \ssSpace)$}{\powerSeriesUniform}
    \timeConversionComment
}{figPowerPsiUniform}

\siFigure{../../power-comparison/images/exp-power-psi-prob-6.pdf}{
    \powerSupportComment{\powerSeriesExp}
    \powerProbComment{$p(\divTimeNum = 1 | \ssSpace)$}{\powerSeriesExp}
    \timeConversionComment
}{figPowerPsiExp}

%% Power dispersion prob results
\siFigure{../../power-comparison/images/old-power-omega-prob-6.pdf}{
    \powerSupportComment{\powerSeriesOld}
    \powerProbComment{$p(\divTimeDispersion < 0.01 | \ssSpace)$}{\powerSeriesOld}
    \timeConversionComment
}{figPowerPsiOld}

\siFigure{../../power-comparison/images/uniform-power-omega-prob-6.pdf}{
    \powerSupportComment{\powerSeriesUniform}
    \powerProbComment{$p(\divTimeDispersion < 0.01 | \ssSpace)$}{\powerSeriesUniform}
    \timeConversionComment
}{figPowerPsiUniform}

\siFigure{../../power-comparison/images/exp-power-omega-prob-6.pdf}{
    \powerSupportComment{\powerSeriesExp}
    \powerProbComment{$p(\divTimeDispersion < 0.01 | \ssSpace)$}{\powerSeriesExp}
    \timeConversionComment
}{figPowerPsiExp}

>>>>

%% Validation accuracy
\siFigure{../../validation/images/validation-accuracy-omega.pdf}{
    \validationAccuracyComparisonCaption{unadjusted}{\divTimeDispersion}
}{figValidationAccuracyOmega}

@@

\siFigure{../../validation/images/validation-accuracy-psi.pdf}{
    \validationAccuracyComparisonCaption{unadjusted}{\divTimeNum}
    \jitterComment
}{figValidationAccuracyPsi}

%% Validation model choice
\siFigure{../../validation/images/validation-model-choice-psi-glm.pdf}{
    \validationModelChoiceComparisonCaption{GLM-adjusted}{$\divTimeNum = 1$}
}{figValidationModelChoicePsiGlm}

@@

%% Power accuracy results
\siSidewaysFigure{../../power-comparison/images/old-power-omega-accuracy-6.pdf}{
    \powerAccuracyComparisonCaption{\powerSeriesOld}
}{figPowerAccuracyOld}

\siSidewaysFigure{../../power-comparison/images/uniform-power-omega-accuracy-6.pdf}{
    \powerAccuracyComparisonCaption{\powerSeriesUniform}
}{figPowerAccuracyUniform}

\siSidewaysFigure{../../power-comparison/images/exp-power-omega-accuracy-6.pdf}{
    \powerAccuracyComparisonCaption{\powerSeriesExp}
}{figPowerAccuracyExp}

%% Power psi results
\siSidewaysFigure{../../power-comparison/images/old-power-psi-6.pdf}{
    \powerComment{\powerSeriesOld}
    \powerPsiComment{\powerSeriesOld}
    \timeConversionComment
}{figPowerPsiOld}

\siSidewaysFigure{../../power-comparison/images/uniform-power-psi-6.pdf}{
    \powerComment{\powerSeriesUniform}
    \powerPsiComment{\powerSeriesUniform}
    \timeConversionComment
}{figPowerPsiUniform}

\siSidewaysFigure{../../power-comparison/images/exp-power-psi-6.pdf}{
    \powerComment{\powerSeriesExp}
    \powerPsiComment{\powerSeriesExp}
    \timeConversionComment
}{figPowerPsiExp}

%% Power dispersion results
\siSidewaysFigure{../../power-comparison/images/old-power-omega-6.pdf}{
    \powerComment{\powerSeriesOld}
    \powerDispersionComment{\powerSeriesOld}
    \timeConversionComment
}{figPowerPsiOld}

\siSidewaysFigure{../../power-comparison/images/uniform-power-omega-6.pdf}{
    \powerComment{\powerSeriesUniform}
    \powerDispersionComment{\powerSeriesUniform}
    \timeConversionComment
}{figPowerPsiUniform}

\siSidewaysFigure{../../power-comparison/images/exp-power-omega-6.pdf}{
    \powerComment{\powerSeriesExp}
    \powerDispersionComment{\powerSeriesExp}
    \timeConversionComment
}{figPowerPsiExp}

%% Power psi probability results
\siSidewaysFigure{../../power-comparison/images/old-power-psi-prob-6.pdf}{
    \powerSupportComment{\powerSeriesOld}
    \powerProbComment{$p(\divTimeNum = 1 | \ssSpace)$}{\powerSeriesOld}
    \timeConversionComment
}{figPowerPsiOld}

\siSidewaysFigure{../../power-comparison/images/uniform-power-psi-prob-6.pdf}{
    \powerSupportComment{\powerSeriesUniform}
    \powerProbComment{$p(\divTimeNum = 1 | \ssSpace)$}{\powerSeriesUniform}
    \timeConversionComment
}{figPowerPsiUniform}

\siSidewaysFigure{../../power-comparison/images/exp-power-psi-prob-6.pdf}{
    \powerSupportComment{\powerSeriesExp}
    \powerProbComment{$p(\divTimeNum = 1 | \ssSpace)$}{\powerSeriesExp}
    \timeConversionComment
}{figPowerPsiExp}

%% Power dispersion prob results
\siSidewaysFigure{../../power-comparison/images/old-power-omega-prob-6.pdf}{
    \powerSupportComment{\powerSeriesOld}
    \powerProbComment{$p(\divTimeDispersion < 0.01 | \ssSpace)$}{\powerSeriesOld}
    \timeConversionComment
}{figPowerPsiOld}

\siSidewaysFigure{../../power-comparison/images/uniform-power-omega-prob-6.pdf}{
    \powerSupportComment{\powerSeriesUniform}
    \powerProbComment{$p(\divTimeDispersion < 0.01 | \ssSpace)$}{\powerSeriesUniform}
    \timeConversionComment
}{figPowerPsiUniform}

\siSidewaysFigure{../../power-comparison/images/exp-power-omega-prob-6.pdf}{
    \powerSupportComment{\powerSeriesExp}
    \powerProbComment{$p(\divTimeDispersion < 0.01 | \ssSpace)$}{\powerSeriesExp}
    \timeConversionComment
}{figPowerPsiExp}
